\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2025-06-11 manuscript/manuscript.tex
addressed question on correction term under H1

Several promising directions for further research emerge from
this study. Firstly, while we used circular block bootstrap, many
other bootstrap variants for serially dependent data, such as the
stationary bootstrap \citep{politis1994stationary} and the dependent wild
bootstrap \citep{shao2010dependent}, could be evaluated under our
correction framework. Secondly, analogous methodologies could be
developed for other goodness-of-fit tests based on empirical
distributions, including the Anderson---Darling and Cramér--von
Mises tests, which are known to outperform the KS test in certain scenarios
\citep{stephens2017tests}. Applying block bootstrap bias correction to
these tests may be particularly beneficial in contexts like extreme
value modeling, where serial dependence is common. Third, it would be
intriguing to extend the proposed NPBB
one-sample KS test to a two-sample setting, allowing for comparison of
marginal distributions without specifying serial dependencies in
either sample. Finally, a rigorous theoretical justification of the
NPBB procedure, including precise conditions for the asymptotic
behavior of the test statistic and the consistency of the bootstrap
approximation, would offer valuable practical insights into the
scenarios where the NPBB approach is expected to perform optimally.

>>>>

Several promising directions for further research emerge from
this study. Firstly, while we used circular block bootstrap, many
other bootstrap variants for serially dependent data, such as the
stationary bootstrap \citep{politis1994stationary} and the dependent wild
bootstrap \citep{shao2010dependent}, could be evaluated under our
correction framework. Secondly, analogous methodologies could be
developed for other goodness-of-fit tests based on empirical
distributions, including the Anderson---Darling and Cramér--von
Mises tests, which are known to outperform the KS test in certain scenarios
\citep{stephens2017tests}. Applying block bootstrap bias correction to
these tests may be particularly beneficial in contexts like extreme
value modeling, where serial dependence is common. Third, it would be
intriguing to extend the proposed NPBB
one-sample KS test to a two-sample setting, allowing for comparison of
marginal distributions without specifying serial dependencies in
either sample. Finally, a rigorous theoretical justification of the
NPBB procedure, including precise conditions for the asymptotic
behavior of the test statistic and the consistency of the bootstrap
approximation, would offer valuable practical insights into the
scenarios where the NPBB approach is expected to perform optimally.
In particular, while the
correction term is designed to calibrate the null distribution of the
test statistic, studying its behavior under alternatives, including
contiguous alternatives, would further inform the power properties of
the method and remains an interesting direction for future research.

### 2025-06-11 manuscript/reply.tex
addressed question on correction term under H1

Thank you for the detailed demonstration. As is standard in hypothesis 
testing, our development of the bootstrap procedure is focused on accurately 
approximating the distribution of the test statistic under the null hypothesis. 
This is consistent with the goal of using the bootstrap to construct valid
p-values and rejection regions. While the same bias correction is applied 
regardless of whether the null is true, its purpose is to replicate the 
behavior of the statistic under the null, which is the basis for valid inference.

>>>>

We thank the reviewer for the detailed demonstration. We would like
clarify that the correction term has the same form as that in
\citet{babu2004goodness}, which is needed in the distribution of the
testing statistic under the null hypothesis. The validity of the test
relies on controlling the Type I error, and thus the justification of
the correction term pertains to the behavior of the statistic
under~$H_0$. The bootstrapping method in \citet{babu2004goodness},
however, cannot be used approximatae the distribution of the null
distribution of the statistic under serial dependence. The
distribution under~$H_1$, particularly under contiguous alternatives,
governs the power of the test but does not affect the correctness of
the null calibration. Our current focus is on ensuring valid inference
under $H_0$, for which the proposed correction is justified. To
address this point, we have added a remark in the \emph{Discussion}
Section, last paragraph, noting that investigation of the test’s
behavior under contiguous alternatives remains of interest but is
distinct from the justification of the correction term.
